% Agradecimentos

\chapter*{Acknowledgments}

First of all, i would like to thank God and the Universe for the opportunity to meet countless wonderful people during the Master's program. I'm glad also for this achievement of personal and professional scope.

I would like to express the deepest appreciation to my advisor Prof. Augusto José Venâncio Neto PhD., who has the attitude and the substance of a genius: he continually and convincingly conveyed a spirit of adventure in regard to research. Without his guidance and persistent help this dissertation would not have been possible. I thank my fellow labmates in UPLAB, LAUT and DIMAP master's lab: Felipe Dantas, Flávio Ramalho, Everton Fagner, Ivanovitch Silva, Daniel Enos, Laudson Souza, Héldon José, Daniel Alencar, José Castillo, Ana Carla, Alessandro Stamatto, Sarah Sakamoto, Eliselma Vieira, José Filho, Handerson Bezerra, Fernando Helton, Adriano Dodó, Waldson Patrício, Aparecida Lopes, Fábio Alexandre,  Romeu Ferreira, Tainá Jesus Medeiros, Indrid Morgane, Havi Batista, Sidney Soares and Romerito Campos, which helped me a lot and I will remember for the rest of my life. 

I would also like to thank everyone who makes up SIG Software, for the opportunity to work on large projects, which has further increased my professional experience. Eespecially,  Chief Executive Officer Raphaella Galhardo and the General Project Manager Gleydson Lima. I should also like to thank Cezar Miranda, who i has had the pleasure of working on highly complex projects.

I am also grateful to the Systems design department team at the Court of Justice of Rio Grande do Norte. Those who have always supported me in this conquest. Especially the division chief Fabiano Silva, and our colleagues, Luan Ribeiro, Paulo Porto, Ítalo Bruno, Vinícius Mikael, Vinícius Leão, Lismaxwell Brito and Tiago Aleixo.

I thank my friends, Joilson Abrantes, Edson Jackson and Danilo Barros. Which always support me.

Last but not the least, I would like to thank my family: my parents , for giving birth to me at the first place and supporting  throughout my life. My grandparents for allways praying for me and supporting me.
